Overview

### 2019-03-19 notebooks/general_info.Rmd
got counts data, starting to plot the data. also wrangled some more data, about 500 packages, which ill pull in soon

What if we roll NULL into every type?
```{r}
los_basic_no_null <- lapply(los_basic, function(lof) {lapply(lof, function(df) {fold_NULL_into_other_types_df(df)})})
```

>>>>

What if we roll NULL into every type?
```{r}
los_basic_no_null <- lapply(los_basic, function(lof) {lapply(lof, function(df) {fold_NULL_into_other_types_df(df)})})

# also curious if we roll raw_NAs in
los_basic_no_null_no_NA <- lapply(los_basic, function(lof) {lapply(lof, function(df) {fold_NULL_and_NA_into_other_types_df(df)})})
```
